%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Fadi}{Younis}{
\href{mailto:fyounis@ryerson.ca}{fadiyounis.atwork@gmail.com} | Toronto | 416.419.2908 |
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Ryerson University}
\descript{M.Sc. in Computer Science (thesis-based)}
\location{June 2018 | Toronto, Ontario \\ Cum. GPA: 4.25/4.33}
Department of Computer Science
\bigbreak
- Taught intro courses in Web Dev, C, MATLAB and R. 
\sectionsep

\subsection{Ryerson University}
\descript{B.Sc. in Computer Science (Honours)}
\location{June 2014 | Toronto, Ontario \\ Cum. GPA: 3.10/4.33}
Department of Computer Science \\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\textbullet{} Github://  \href{https://github.com/FadiSYounis}{\custombold{FadiSYounis}} \\
\textbullet{} LinkedIn://  \href{https://ca.linkedin.com/in/fadiyounis}{\custombold{fadiyounis}} \\
\textbullet{} Research Gate://\href{https://www.researchgate.net/profile/Fadi_Younis3}{\custombold{fadiyounis3}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Secure Computing\\
Web-Services Software Engineering\\
Advanced Database Systems \\
Soft Computing and Machine Intelligence \\
Machine Learning and Statistical Learning \\
Independent Directed Studies
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\location{Over 10,000 Lines:}
\textbullet{} Python \textbullet{} R \textbullet{} SQL \textbullet{}  MATLAB
\bigbreak
\location{Technologies and Frameworks:}
\textbullet{} Eclipse \textbullet{} Tensorflow \textbullet{} NLP
\bigbreak
\location{Familiar With:}
\textbullet{} C++ \textbullet{} GO \textbullet{} Django
\section{Recognition}
\subsection{Awards}
\textbullet{} Nominated For the Governor General Gold Medal (GGGM) - 2018
\bigbreak
\textbullet{} Receiver of the MITACS Accelerate Grant - 2017
\bigbreak
\textbullet{} Receiver of the Ontario Graduate Scholarship Program (OGS) - 2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{IG2 Group Inc.}
\descript{| Graduate Researcher Intern | Full-Stack}
\location{Jan 2017 - Jan 2018 | Toronto, Ont. }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Worked with fellow researchers to implement a proprietary patent on Encrypted Search through the MITACS innovation research grant\\
\item Patent - Efficient Computations on Encrypted Data Stored in the Cloud (https://www.mitacs.ca/en/projects/efficient-computations-encrypted-data-stored-cloud)
\item Tools Used - Python, Djnago, Bash, Flask, 3-rd party Encryption Libraries.
\end{tightemize}
\sectionsep

\runsubsection{Ontario Government}
\descript{| Application Developer and Analyst}
\location{Jan 2014 – Feb 2015 | Toronto, Ont. }
\begin{tightemize}
\item Independently designed and implemented the v1 of a log filter to analyze government specific Apache server log files targeted for usage by senior management. The application was built using the Java Enterprise. 
\item Designed and wrote repeatable tests for the log filter and other applications using the JUnit testing framework on the Eclipse development environment.
\item  Documented hundreds of usability bugs with accurate technical descriptions and provided comprehensive but concise steps to reproduce them.
\item Performed Unit acceptance testing (UAT) on proprietary government software projects to find faults in the business documentation, application design, and overall performance.
\item Tools Used - Java SE, Bash, JUnit, Eclipse, 3-rd party JSON libraries.
\end{tightemize}
\sectionsep

\runsubsection{Projects}
\descript{| Personal and Academic }
\location{Below are the ones highlighted. Visit my profile (FadiSYounis) for details.}
\begin{tightemize}
\item Ubuntu Miner (Ruby), Mines the entire Ubuntu OS for source code - Academic
\item World's Smallest Blockchain (Java), Blockchain Chain generated in Java - Personal
\item CV/Resume (Latex), Built my resume in Latex because it better - Personal
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications and Research}
\runsubsection{ACM Journal Paper - In Progress}
\descript{| July 2018 }
\location{Using Honeypots In A Decentralized Framework To Defend Against Adversarial Machine-Learning Attacks}
\begin{tightemize}
\item Under the supervision of \textbf{Dr. Ali Miri, Ph.D, P.Eng.} I completed my research and defended my thesis in the area of Adversarial Machine-Learning. This journal paper represents a summary of my thesis findings. 
\item Thesis Dissertation - https://goo.gl/KMqdzb
\item Thesis Conference paper (draft) - https://goo.gl/WfBUcg
\end{tightemize}
\sectionsep

\runsubsection{IEEE Conference Paper - Publication accepted}
\descript{| July 2017 }
\location{An Analysis of the Security of Compressed Sensing Using an Artificial Neural Network}
\begin{tightemize}
\item Worked with \textbf{Shadan Ghaffari}, \textbf{Dr. Wilson Poon} and Professor \textbf{Ali. Miri}, We showed that, using a neural network, we can predict the key to decrypt the data and reveal valuable information about the data stored.
\item Published at the \textit{Privacy, Security and Trust} (PST) conference at the UofCalgary
\item Conference paper - https://goo.gl/fKGPwA
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}